Geometron: A Language for Graphical Communication

### 2018-09-08 paper1.tex
paper update

    Our existing theoretical models for understanding new machines tend to ignore how machines propagate through the human population, but I believe this is a mistake.  These questions get banished from technical theoretical problems because we have arbitrarily divided who thinks about what problems up into``engineering",``humanities",``marketing", etc.  We like to think that quantum computing will either succeed or fail based on some intrinsic technical merit, but none of us will ever succeed in this venture without clear communication between the advocates of the technology and the sponsors(funding agents, investors, upper managers).  Those people expect very simple and clear stories to be told in a mostly graphical format via PowerPoint, and that story must be more compelling than that of competing technologies.  Thus clear graphical communication is fundamental to the very survival of a new technology.

@@

\includegraphics{figures/figure1_cubes.png}

@@

\begin{figure}
\includegraphics{figures/fig2cubestack.png}
\caption{Tablet layers.}
\end{figure}

@@

\begin{figure}
\includegraphics{figures/figure3_bottomTablet.png}

@@

\begin{figure}
\includegraphics{figures/figure4_asciitablet.png}
\caption{First tablet from bottom: top of 7 bit ASCII.  Backspace at 0177 is excluded and replaced by a ``do nothing'' action.  Hence range is from ``at'' symbol(0100) through tilde(0176), or 0x40-0x7E hexidecimal.}
\end{figure}

@@

\includegraphics{figures/figure5_shapetable.png}

@@

\includegraphics{figures/figure6_actionTablet.png}

@@

\begin{figure}
\includegraphics{figures/figure7_globalCursor.png}
\caption{Global graphical cursor}
\end{figure}

@@

\begin{figure}
\includegraphics{figures/figure8_symmetries.png}
\caption{Basic symmetry groups.  These glyphs correspond to setting the angle step to be 90 degrees($\frac{\pi}{2}$ radians), 72 degrees($\frac{\pi}{5}$ radians), or 60 degrees($\frac{\pi}{6}$ radians). Their addresses are 0304, 0305, and 0306. }
\end{figure}

@@

\includegraphics{figures/figure9_scales.png}

@@

\section{
3. Examples}

@@

\section{
4. Structure of Code}

@@

    Public domain graphics library for quantum information science

    Working with MS office suite workflow

    Working with Adobe Illustrator and Inkscape

@@

\section{
Future Work and Potential Impact}

>>>>

    Our existing theoretical models for understanding new machines tend to ignore how machines propagate through the human population, but I believe this is a mistake.  These questions get banished from technical theoretical problems because we have arbitrarily divided who thinks about what problems up into ``engineering", ``humanities", ``marketing", etc.  We like to think that quantum computing will either succeed or fail based on some intrinsic technical merit, but none of us will ever succeed in this venture without clear communication between the advocates of the technology and the sponsors(funding agents, investors, upper managers).  Those people expect very simple and clear stories to be told in a mostly graphical format via PowerPoint, and that story must be more compelling than that of competing technologies.  Thus clear graphical communication is fundamental to the very survival of a new technology.

@@

\includegraphics[width=\linewidth]{figures/figure1_cubes.png}

@@

\begin{figure}
\includegraphics[width=\linewidth]{figures/fig2cubestack.png}
\caption{Tablet layers.}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{figures/figure3_bottomTablet.png}

@@

\begin{figure}
\includegraphics[width=\linewidth]{figures/figure4_asciitablet.png}
\caption{First tablet from bottom: top of 7 bit ASCII.  Backspace at 0177 is excluded and replaced by a ``do nothing'' action.  Hence range is from ``at'' symbol(0100) through tilde(0176), or 0x40-0x7E hexidecimal.}
\end{figure}

@@

\includegraphics[width=\linewidth]{figures/figure5_shapetable.png}

@@

\includegraphics[width=\linewidth]{figures/figure6_actionTablet.png}

@@

\begin{figure}
\includegraphics[width=\linewidth]{figures/figure7_globalCursor.png}
\caption{Global graphical cursor}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{figures/figure8_symmetries.png}
\caption{Basic symmetry groups.  These glyphs correspond to setting the angle step to be 90 degrees($\frac{\pi}{2}$ radians), 72 degrees($\frac{\pi}{5}$ radians), or 60 degrees($\frac{\pi}{6}$ radians). Their addresses are 0304, 0305, and 0306. }
\end{figure}

@@

\includegraphics[width=\linewidth]{figures/figure9_scales.png}

@@

\section{Examples}

@@

\section{Structure of Code}

@@

There are two ways to parse the work flow of the Geometron system.  We can consider the path taken by a new user, which is what is sketched in the above paragraph.  In this flow, a new user starts out seeing this as just a free graphics library, then moves up to making their own graphics, and finally to building their own graphics languages.  The other way to consider the work flow is to trace the path of the information as it would flow for an expert user.  In this path, a Geometron instance is created by cloning all the code using the script replicator.php onto a new directory on a web server with PHP istalled.

create new instance:
replicator.php
navigate to glyph editor, test:
index.php
go to tree, create a new branch on it:
tree.php
go to that branch and start editing it:
index.php?path=mynewpath/
edit the shape table:
shapetableeditor.php?path=mynewpath/
shapes.txt
pastebin.com 
actions, then symbols
index.php?path=mynewpath/
(PUBLISH)
svg/svg[datecode].svg --> web, adobe creative suite, microsoft office suite, inkscape
(PNG PUBLISH)
save as: filename.png --> powerpoint, word, latex, web
web links--> svgfeed.php --> index.php?path=mynewpath/&url=mynewpath/svg/svg[datecode].svg

@@

\section{Future Work and Potential Impact}
